### 2011-11-06 doc/pldi2012/type_system.tex
intro
Making some minor changes to the type system section

\section{Type System}

@@

Table~\ref{tbl:priv_const} shows the form of the individual privileges and
constraints that make up $\Phi$ and $C$.  Privileges represent the ability to
perform some operation on a region (or, as we will see, on any of its
subregions).  Constraints are used to capture the subregion relationships that
result from partitioning ($a \prec b$ if $a$ was a result of a partitioning of
$b$), the more general anywhere-in-the-subregion-tree relationship ($a \le b$ if $a$ equals $b$ or is either a direct or indirect subregion), and equality (or
inequality) of integer expressions.  More complicated constraints can be formed
through conjunctions, but neither negation nor disjunctions are permitted.  For
an example of how these work, here is the typing rule for reading an element
from a region:

@@

This rule tells us that in order to read from a pointer, we must be able to
provide a region ($r_2$ in this case) for which we possess read privilege that 
is known to either be, or contain, the region to which the pointer is
constrained.  Similar rules exist for the other four region access operations.

@@

Any expression whose type is a region relationship can be unpacked.  Doing so
introduces a fresh region variable for each region that was bound in the 
quantification.  The fresh region variables are substitued into the region
relaionship's type, and a corresponding substituion is performed on the
constraints that were captured by the region relationship.  These substituted
constraints are added to the current function's (flow-sensitive) constraints.

@@

Although the type system uses explicit packing and unpacking operations, they 
are implicit in the Legion application code.  Unpacking operations are 
automatically inserted whenever a variable comes into scope.  Packing operations
are attemped whenever a variable is written to memory or passed as an argument
to a function.  Additionally, the simultaneous assignment operation essentially
performs a pack for the result of the assignments and will also perform an
unpack if one ore more fields of the structure are left unchanged.

@@

Region access privileges cannot be stored or packed.  Instead, they follow the
function call tree, and it is this property that allows the runtime to make
its scheduling decisions in a distributed way.  The original source of any
privilege for a given region is the \emph{newrr} operation that created that
region, but the way in which privileges can be provided to a subtask, or
returned to a parent task, is described in the function application rule:

@@

In this rule, expression $e_1$ has the type of a Legion function.  In addition
to the function's input and output types, it specifies the privileges and
constraints that must exist at the point where the function is called.  It also
describes the privileges and constraints that exist as post-conditions of the
function invocation.  The output type, privileges, and constraints can be
captured in an existential quantification, allowing a function to return one
or more regions that were previously unknown to the caller.

>>>>

\section{Type System}
\label{sec:type}

@@

Table~\ref{tbl:priv_const} shows the form of the individual privileges and
constraints that make up $\Phi$ and $C$.  Privileges represent the ability to
perform some operation on a region (or, as we will see, on any of its
subregions).  Constraints are used to capture the subregion relationships that
result from partitioning ($a \prec b$ if $a$ was a result of a partitioning of
$b$), the more general anywhere-in-the-subregion-tree relationship ($a \le b$ if $a$ equals $b$ or is either a direct or indirect subregion), and equality (or
inequality) of integer expressions.  More complicated constraints can be formed
through conjunctions, but neither negation nor disjunctions are permitted.  For
an example of how these work, below is the typing rule for reading an element
from a region:

@@

This rule tells us that in order to read from a pointer, we must be able to
provide a region ($r_2$ in this case) for which we possess a read privilege that 
is known to either be, or contain, the region to which the pointer is
constrained.  Similar rules exist for the other four region access operations.

@@

Any expression whose type is a region relationship can be unpacked.  Doing so
introduces a fresh region variable for each region that was bound in the 
quantification.  The fresh region variables are substitued into the region
relaionship's type, and a corresponding substituion is performed on the
constraints that were captured by the region relationship.  These substituted
constraints are added to the current task's (flow-sensitive) constraints.

@@

Although the type system uses explicit packing and unpacking operations, they 
are implicit in the Legion application code.  Unpacking operations are 
automatically inserted whenever a variable comes into scope.  Packing operations
are attemped whenever a variable is written to memory or passed as an argument
to a task.  Additionally, the simultaneous assignment operation essentially
performs a pack for the result of the assignments and will also perform an
unpack if one ore more fields of the structure are left unchanged.

@@

Region access privileges cannot be stored or packed.  Instead, they follow the
task call tree, and it is this property that allows the runtime to make
its scheduling decisions in a distributed way.  The original source of any
privilege for a given region is the \emph{newrr} operation that created that
region, but the way in which privileges can be provided to a subtask, or
returned to a parent task, is described in the task application rule:

@@

In this rule, expression $e_1$ has the type of a Legion task.  In addition
to the task's input and output types, it specifies the privileges and
constraints that must exist at the point where the task is called.  It also
describes the privileges and constraints that exist as post-conditions of the
task invocation.  The output type, privileges, and constraints can be
captured in an existential quantification, allowing a task to return one
or more regions that were previously unknown to the caller.
